---
title: "临时存放的笔记"
output: 
  pdf_document: 
    extra_dependencies:
      ctex: UTF8  
    latex_engine: xelatex
    number_sections: yes
    toc: yes
classoption: "b5paper"
---

```{r setup, include=FALSE}
knitr::knit_hooks$set(
  optipng = knitr::hook_optipng,
  pdfcrop = knitr::hook_pdfcrop,
  small.mar = function(before, options, envir) {
    # smaller margin on top and right
    if (before) par(mar = c(4.1, 4.1, 0.5, 0.5), family = "Times")  
  }
)
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  echo = TRUE,
  cache = TRUE,
  small.mar = TRUE,
  out.width = "70%",
  fig.align = "center",
  fig.width = 6,
  width = 69,
  fig.asp = 0.618
)
is_on_travis = identical(Sys.getenv("TRAVIS"), "true")
is_online = curl::has_internet()
options(
  digits = 3,
  citation.bibtex.max = 999,
  bitmapType = "cairo",
  stringsAsFactors = FALSE,
  BioC_mirror = "https://mirrors.tuna.tsinghua.edu.cn/bioconductor",
  repos = c(
    CRAN = if(is_on_travis) "https://cloud.r-project.org" else "https://mirrors.tuna.tsinghua.edu.cn/CRAN/",
    RForge = "https://r-forge.r-project.org",
    inla = "https://inla.r-inla-download.org/R/stable"
  ),
  knitr.graphics.auto_pdf = FALSE,
  width = 69,
  str = strOptions(strict.width = "cut"),
  tikzDefaultEngine = "pdftex",
  tikzLatexPackages = c(
    "\\usepackage{tikz}",
    "\\usepackage[active,tightpage,psfixbb]{preview}",
    "\\PreviewEnvironment{pgfpicture}",
    "\\setlength\\PreviewBorder{0pt}",
    "\\usepackage[colorlinks, breaklinks]{hyperref}",
    "\\usepackage{amsmath,amsfonts,mathrsfs,times}"
  )
)
lapply(c('tikzDevice','car','IM'), function(pkg) {
  if (system.file(package = pkg) == '') install.packages(pkg)
})
```

# 前言 {#preface}

统计图形：图形中一定有统计方法，如平滑、回归、残差等统计意义或者能揭示数据中的某种趋势规律，否则只是一个图而已，重点一定在图所展示的内容上。否则，只能说是数据可视化，因为它更强调绘图技法，视觉效果

支持缩放和拖拽的交互可视化三维地球上

- Building an Interactive Globe Visualization in R [threejs][r-threejs]
- Help Us [Map TrumpWorld][map-trump]
- Trumpworld Analysis: Ownership Relations in his [Business Network][analysis-trump]
- Global cycling and running heatmap [全球循环][global-cycling]和运行轨迹
- Google maps street-level air quality using Street View cars with sensors 可视化街区[空气质量][air-quality]
- High-detail [landscape][high-detail-landscape] using lidar data 激光雷达数据展示高清细节
- [Mapping With Sf][mapping-sf] 画地图 sf
- Plotting 3D maps and [location tracks][location-tracks] 基于 GPS 数据的三维轨迹追踪 
- [Mapping oil][map-oil] production by country in R 石油产量在全球的分布
- How to [highlight countries][highlight-countries] on a map 高亮地图上的国家
- New Zealand election and [census][new-census] 新西兰大选和普查数据 [nzelect][nzelect] 数据接口
- 新西兰大选预测 New Zealand general [election forecasts][election-forecasts] 广义可加模型
- Social Network Analysis and Topic Modeling [链接1][codecentric-blog] [链接2][topic-modeling] - Social Network Analysis and Topic Modeling of codecentric’s Twitter friends and followers [链接3][codecentric-twitter]

- <http://www.htmlwidgets.org/> R 与 JavaScript
- <https://github.com/rich-iannone/DiagrammeR>
- 分析 <https://github.com/igraph/python-igraph> 与 <https://github.com/igraph/rigraph>
Intro to Geospatial Data with R <http://www.datacarpentry.org/r-raster-vector-geospatial/>




```{r child = 'ch1/rmarkdown.Rmd'}
```

[codecentric-blog]: https://blog.codecentric.de/en/2017/01/topic-modeling-codecentric-blog-articles/
[topic-modeling]: https://blog.codecentric.de/en/2017/07/combining-social-network-analysis-topic-modeling-characterize-codecentrics-twitter-friends-followers/
[codecentric-twitter]: https://shiring.github.io/text_analysis/2017/07/28/codecentric_twitter
[election-forecasts]: https://ellisp.github.io/elections/elections.html
[nzelect]: https://github.com/ellisp/nzelect
[new-census]: https://ellisp.github.io/blog/2017/04/25/more-cartograms
[highlight-countries]: http://sharpsightlabs.com/blog/highlight-countries-on-map/
[map-oil]: http://sharpsightlabs.com/blog/map-oil-production-country-r/
[location-tracks]: https://shiring.github.io/maps/2017/04/09/gran_canaria
[mapping-sf]: https://ryanpeek.github.io/2017-11-21-mapping-with-sf-part-3/
[high-detail-landscape]: http://flowingdata.com/2017/12/04/high-detail-landscape-using-lidar-data/
[air-quality]: http://flowingdata.com/2017/11/08/google-maps-street-level-air-quality-using-street-view-cars-with-sensors/
[global-cycling]: http://flowingdata.com/2017/11/21/global-cycling-and-running-heatmap/
[map-trump]: https://www.buzzfeed.com/johntemplon/help-us-map-trumpworld
[analysis-trump]: https://lucidmanager.org/trumpworld-analysis/
[r-threejs]: https://www.displayr.com/interactive-globe-r/
